Is it time for an NBA expansion?

### 2024-04-19 paper/paper.qmd
Created New Graphs

library(tidyverse)
library(readr)
library(modelsummary)
library(tinytex)
```

@@

@@

# Now remove less important columns
full_nba_data <- combined_data %>%
  select(-G, -MP, -`2P`, -`2PA`, -`2P%`, -Rk)

@@

# Saving Clean Data
write.csv(nba_data, "../data/clean_data/nba_data.csv", row.names = FALSE)
write.csv(full_nba_data, "../data/clean_data/full_nba_data.csv", row.names = FALSE)
```

@@

>>>>

library(tidyverse)
library(readr)
library(modelsummary)
library(tinytex)
library(lubridate)
```

@@

lebron_data <- read_csv("../data/raw_data/NBA_Lebron_James.csv")
scoring_data <- read.csv("../data/raw_data/All_time_Scoring.csv")

@@

# Now remove less important columns
full_nba_data <- combined_data %>%
  select(-G, -MP, -Rk)

@@

# Saving Clean Data
write.csv(nba_data, "../data/clean_data/nba_data.csv", row.names = FALSE) #Only League Averages
write.csv(full_nba_data, "../data/clean_data/full_nba_data.csv", row.names = FALSE) #All Teams

scoring_data$Date <- as.Date(scoring_data$Date)

scoring_data$Year <- year(scoring_data$Date) +
  ifelse(month(scoring_data$Date) > 8 | 
         (month(scoring_data$Date) == 8 & day(scoring_data$Date) > 12), 1, 0)
```

@@

ggplot(scoring_data, aes(x = Year_Modified, fill = factor(Year_Modified))) +
  geom_histogram(stat = "count", binwidth = 1, color = "black") +
  labs(title = "Frequency of Records by Year",
       x = "Year",
       y = "Count of Records",
       fill = "Year") +
  theme_minimal() +
  theme(legend.position = "none")
##
data_1980_onwards <- scoring_data %>%
  filter(Year_Modified >= 1980)

# Create histogram for count of records per year from 1980 onwards
ggplot(data_1980_onwards, aes(x = Year_Modified)) +
  geom_histogram(stat = "count", bins = length(unique(data_1980_onwards$Year_Modified)), fill = "blue", color = "black") +
  labs(title = "Count of Records per Year from 1980 Onwards",
       x = "Year Modified",
       y = "Count of Records") +
  theme_minimal()

##
data_1980_60pts_plus <- scoring_data %>%
  filter(Year_Modified >= 1980, PTS >= 60)

# Create histogram for count of records per year for scores of 60 or more from 1980 onwards
ggplot(data_1980_60pts_plus, aes(x = Year_Modified)) +
  geom_histogram(stat = "count", bins = length(unique(data_1980_60pts_plus$Year_Modified)), fill = "red", color = "black") +
  labs(title = "Count of Records per Year for Scores of 60+ PTS from 1980 Onwards",
       x = "Year Modified",
       y = "Count of Records") +
  theme_minimal()
```
